---
title: "{{{ vignette_title }}}"
author: 
  - name: Your name
    affiliation:
    - Your institution
    email: your.email@somewhere.com
output: 
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: show
date: "`r doc_date()`"
package: "`r pkg_ver('{{ Package }}')`"
vignette: >
  %\VignetteIndexEntry{{{ braced_vignette_title }}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    crop = NULL ## Related to https://stat.ethz.ch/pipermail/bioc-devel/2020-April/016656.html
)
```

# Basics

## Install `{{ Package }}`

You can install `r Biocpkg("{{ Package }}")` by using the following commands in your `R` session:

```{r "install", eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
      install.packages("BiocManager")
  }

BiocManager::install("{{ Package }}")

## Check that you have a valid Bioconductor installation
BiocManager::valid()
```

## Asking for help

Ask for help at [Bioconductor support site](https://support.bioconductor.org/). Remember to use the `{{ Package }}` tag and check [the older posts](https://support.bioconductor.org/tag/{{ Package }}/). Other alternatives are available such as creating GitHub issues and tweeting. However, please note that if you want to receive help you should adhere to the [posting guidelines](http://www.bioconductor.org/help/support/posting-guide/).

## Citing `{{ Package }}`

We hope that `r Biocpkg("{{ Package }}")` will be useful for your research. Please use the following information to cite the package and the overall approach. Thank you!

```{r "citation"}
## Citation info
citation("{{ Package }}")
```

# Quick start to using `{{ Package }}`

```{r "start", message=FALSE}
library("{{ Package }}")
```


`R` session information.

```{r reproduce3, echo=FALSE}
## Session info
library("sessioninfo")
options(width = 120)
session_info()
```
